Outline of Ideas for BTC Transaction Frequency

### 2015-10-16 outline/outline.tex
Added a couple details about the quality of the probability estimates under various counterfactuals.

Given\footnotetext{Cite RStan} an approximate simulation of the posterior distribution of the model parameters, we can use Monte Carlo simulation to estimate the probability of a block filling up in a number of ways. The simplest way is to compute parameter estimates based on the posterior, e.g. posterior means or posterior medians, then estimate the probability of a block filling up by simulating the model conditional on these parameter values. In order to take into account increased Bitcoin usage, we can manually increase the mean transaction data rate parameter, $\gamma$, while holding other parameters constant. In order to take into account seasonality, we can make $\gamma$ change in a predictable, seasonal pattern.

This approach has two major shortfalls: 1) it ignores parameter uncertainty, and 2) it assumes that the other parameters will remain constant as $\gamma$ increases. We can mitigate 1) while making 2) if not worse, different. Specifically, given access to an approximate simulation of the posterior of the model parameters, we can simulate the model for each draw from the posterior in order to estimate the probability of a block filling up --- this is the posterior predictive distribution.\footnote{Cite Gelman et al. text here} In order to allow for different transaction rates in this simulation, we can set $\gamma$ at a particular value while using the full posterior of the other model parameters, or even better we can shift the posterior of $\gamma$ so that the posterior mean of the shifted posterior is a desired value. This approach takes into account parameter uncertainty but assumes that our uncertainty about the other parameters would be unchanged if the location of $\gamma$'s distribution were different. We estimate the probability of a block filling using all three approaches, but because of the required assumptions the estimates become less credible for values of $\gamma$ or $\mathrm{E}[\gamma]$ further away from the estimated values.

>>>>

Given\footnotetext{Cite RStan} an approximate simulation of the posterior distribution of the model parameters, we can use Monte Carlo simulation to estimate the probability of a block filling up in a number of ways. The simplest way is to compute parameter estimates based on the posterior, e.g. posterior means or posterior medians, then estimate the probability of a block filling up by simulating the model conditional on these parameter values. In order to take into account increased Bitcoin usage, we can manually increase the mean transaction data rate parameter, $\gamma$, while holding other parameters constant. In order to take into account seasonality, we can make $\gamma$ change in a predictable, seasonal pattern. This approach directly specifies the mean transaction rate at $\gamma$, but because of the mean-variance relationship of the gamma distribution it also indirectly specifies the variance of the transaction rate at $\gamma/\hat{beta}$ where $\hat{\beta}$ is an estimate of $\beta$.

This approach has two major shortfalls: 1) it ignores parameter uncertainty, and 2) it assumes that the other parameters will remain constant as $\gamma$ increases. We can mitigate 1) while making 2) if not worse, different. Specifically, given access to an approximate simulation of the posterior of the model parameters, we can simulate the model for each draw from the posterior in order to estimate the probability of a block filling up --- this is the posterior predictive distribution.\footnote{Cite Gelman et al. text here} In order to allow for different transaction rates in this simulation, we can set $\gamma$ at a particular value while using the full posterior of the other model parameters, or even better we can shift the posterior of $\gamma$ so that the posterior mean of the shifted posterior is the desired value. This approach takes into account parameter uncertainty but assumes that our uncertainty about the other parameters would be unchanged if the location of $\gamma$'s distribution were different. Essentially this requires that if we were in a higher transaction rate regime, our priors would have been different such that the posterior distribution would have obtained would be the shifted posterior we construct. Explicitly constructing this prior would be involved and maybe intractable or even impossible. Instead we estimate the probability of a block filling using all three approaches, but acknowledge that the estimates become less credible for values of $\gamma$ or $\mathrm{E}[\gamma]$ further away from their estimated values.
